\documentclass[letterpaper, 10pt]{article}

\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage[top=0.5in, bottom=0.5in, left=0.7in, right=0.7in]{geometry}

\pagestyle{empty}

\begin{document}

%----------HEADING----------
\begin{center}

\textbf{\LARGE Debosmita Mukhopadhyay} \\ \vspace{2pt}

\href{mailto:debosmita_mukhopadhyay@srm.edu.in}{\underline{debosmita_mukhopadhyay@srm.edu.in}} $|$
\href{https://github.com/debosmita-03}{\underline{github.com/debosmita-03}}
\href{https://github.com/debosmita-03}{\underline{github.com/debosmita-03}}

\end{center}

%-----------TECHNICAL SKILLS-----------
\section*{Technical Skills}
\hrule
\vspace{4pt}

\begin{itemize}

\item[] \textbf{Programming}: C, C++, Java, Python

\item[] \textbf{Frameworks \& Tools}: MERN Stack Development, Git, GitHub

\item[] \textbf{Languages}: English, Bengali, Hindi

\item[] \textbf{Other Skills}: AI/ML

\end{itemize}

%-----------EXPERIENCE-----------
\section*{Experience}
\hrule
\vspace{4pt}

\begin{itemize}

\item[]
\textbf{Intern} \hfill May 2026 -- Present \\

\textit{India Space Lab} \hfill \textit{India}

\begin{itemize}
\item Worked on AI and software development related projects.
\item Collaborated with team members on technical tasks and development.
\end{itemize}

\item[]
\textbf{Infosys Springboard Internship} \hfill Dec 2025 -- Mar 2026 \\

\textit{Infosys Springboard} \hfill \textit{India}

\begin{itemize}
\item Worked on technical learning modules and project-based tasks.
\item Improved programming and development skills through practical assignments.
\end{itemize}

\item[]
\textbf{Product Management Intern} \hfill Aug 2025 -- Oct 2025 \\

\textit{IIT Guwahati} \hfill \textit{India}

\begin{itemize}
\item Contributed to product management and project coordination activities.
\item Worked on planning, documentation, and team collaboration tasks.
\end{itemize}

\end{itemize}

%-----------SELECTED PROJECTS-----------
\section*{Selected Projects}
\hrule
\vspace{4pt}

\begin{itemize}

\item[]
\textbf{Weather Forecasting App}

\begin{itemize}
\item Developed an application to predict and display weather conditions.
\item Used API integration for real-time forecasting.
\end{itemize}

\item[]
\textbf{Obstacle Management Robot}

\begin{itemize}
\item Built a robot capable of detecting and avoiding obstacles.
\item Worked on sensor integration and movement control.
\end{itemize}

\item[]
\textbf{Jarvis - Personal AI Assistant}

\begin{itemize}
\item Created an AI assistant capable of performing voice-based tasks.
\item Implemented automation and command execution features.
\end{itemize}

\item[]
\textbf{Auto Reply Chatbot}

\begin{itemize}
\item Developed a chatbot for automated responses.
\item Used AI/ML concepts for smart conversation handling.
\end{itemize}

\end{itemize}

%-----------HONORS & AWARDS-----------
\section*{Honors \& Awards}
\hrule
\vspace{4pt}

\begin{itemize}

\item[] AMD AI Sprint Hackathon Participant

\item[] Internship Completion Certificate

\end{itemize}

%-----------EDUCATION-----------
\section*{Education}
\hrule
\vspace{4pt}

\begin{itemize}

\item[]
\textbf{Class 10} \hfill 89\%

\item[]
\textbf{Class 12} \hfill 94.8\%

\item[]
\textbf{Bachelor's Degree in Computer Science}

Current GPA (Until 3rd Semester): 9.03

\end{itemize}

%-------------------------------------------

\end{document}